---
title: "Quarto Computations"
format: 
  html: 
    code-fold: true
    code-link: true
    code-tools: true
---

This dataset contains a subset of the fuel economy data from the EPA.
Specifically, we use the `mpg` dataset from the **ggplot2** package.

```{r}
#| label: load-packages
#| echo: false

library(ggplot2)
library(tibble)
library(dplyr)
```

The visualization below shows a positive, strong, and linear relationship between the city and highway mileage of these cars.
Additionally, mileage is higher for cars with fewer cylinders.

@fig-scatterplot shows a positive, strong, and linear relationship between the city and highway mileage of these cars.

```{r}
#| label: fig-scatterplot
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-alt: "Scatterplot of city vs. highway mileage for cars, where points are colored by the number of cylinders. The plot displays a positive, linear, and strong relationship between city and highway mileage, and mileage increases as the number of cylinders decreases."
#| fig-width: 6
#| fig-height: 3.5

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()
```

```{r jlkd}
num_workers <- 1000
execs <- 200
salary <- 
  tibble::tibble(
    Status = c(rep("Exec", execs), 
               rep("Employee", num_workers - execs)),
    Salary = c(sample(500:1000, execs, TRUE), 
               sample(30:100, num_workers - execs, TRUE))
  )
```


```{r}
rate = 0.5/ 100
sal_mult = 4
salary %>% 
  mutate(Death_Status = ifelse(runif(length(Salary)) < rate, 1, 0),
         Claim = ifelse(Death_Status == 1, sal_mult * Salary, 0)
         ) %>% 
  group_by(Status) %>% 
  summarise(total = sum(Claim),
            num_claims = sum(Death_Status))
```

